Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-17 article/draft.tex
add abstract

>>>>

\section*{Abstract}

There is growing pressure for mainstream platforms, such as Facebook, Twitter or YouTube, to moderate the available content. 
Collecting social media data via API and scraping, we investigated their interventions through a series of examples. 
These interventions can be classified into three broad categories: 
(i) temporary or permanent suspension of users, 
(ii) introducing flags and notices, and 
(iii) reducing the visibility of some content. 
Use cases belonging to each category will be shown for Facebook, Twitter and YouTube. 
Finally, we discuss how an increased effort of transparency can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
